---
title: "Project Overview"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
source("R/read_manifest.R")
source("R/read_summary.R")
source("R/tables.R")

result_dir <- get_result_dir("data")
if (!dir.exists(result_dir) || !file.exists(file.path(result_dir, "manifest.json"))) {
  stop("Pipeline output not found. Set SCRNASEQ_REPORT_DATA or link/copy results to report/data/")
}

manifest <- read_manifest(result_dir)
step_table <- render_steps_table(manifest)
success_steps <- if (nrow(step_table) > 0) sum(tolower(step_table$status) == "success") else 0
```

<div class="report-kicker">scRNA-seq analysis report</div>

<div class="report-lede">
This report summarizes the single-cell RNA-seq analysis generated by <strong>scRNAseqMulticommand</strong>, using the same report shell and visual language as the RNAFlow report template.
</div>

::: {.metric-grid}
::: {.metric-card}
[Project]{.metric-label}

[`r manifest$project_name`]{.metric-value}

[Pipeline `r manifest$pipeline_version`]{.metric-note}
:::

::: {.metric-card}
[Samples]{.metric-label}

[`r length(manifest$samples)`]{.metric-value}

[`r paste(manifest$samples, collapse = ", ")`]{.metric-note}
:::

::: {.metric-card}
[Groups]{.metric-label}

[`r length(manifest$groups)`]{.metric-value}

[`r paste(manifest$groups, collapse = ", ")`]{.metric-note}
:::

::: {.metric-card}
[Cells]{.metric-label}

[`r manifest$metrics$total_cells %||% "N/A"`]{.metric-value}

[Cell metadata records]{.metric-note}
:::

::: {.metric-card}
[Integration]{.metric-label}

[`r manifest$integration_method`]{.metric-value}

[Species TaxID `r manifest$species_tax_id`]{.metric-note}
:::

::: {.metric-card}
[Completed Steps]{.metric-label}

[`r success_steps`]{.metric-value}

[`r nrow(step_table)` tracked steps]{.metric-note}
:::
:::


## Project Summary

| Field | Value |
|------|-------|
| **Project** | `r manifest$project_name` |
| **Pipeline Version** | `r manifest$pipeline_version` |
| **Species TaxID** | `r manifest$species_tax_id` |
| **Integration Method** | `r manifest$integration_method` |
| **Run Timestamp** | `r manifest$run_timestamp` |
| **Total Cells** | `r manifest$metrics$total_cells %||% "N/A"` |
| **Samples** | `r paste(manifest$samples, collapse = ", ")` |
| **Groups** | `r paste(manifest$groups, collapse = ", ")` |

## Pipeline Steps

```{r steps-table}
knitr::kable(render_steps_table(manifest), format = "html")
```

## Sample Cell Counts

```{r sample-counts}
samples <- render_count_table(manifest$metrics$samples)
if (nrow(samples) > 0) {
  knitr::kable(samples, format = "html")
} else {
  cat("No sample-level cell counts recorded.")
}
```

## Final Outputs

```{r final-objects}
if (!is.null(manifest$final_objects) && length(manifest$final_objects) > 0) {
  objs <- if (is.data.frame(manifest$final_objects)) manifest$final_objects else do.call(rbind, lapply(manifest$final_objects, as.data.frame, stringsAsFactors = FALSE))
  knitr::kable(objs, format = "html")
} else {
  cat("No final output objects recorded in manifest.")
}
```
